---
title: "Gradient Descent"
description: 경사하강법을 통해 최적의 모수를 찾아내자.

author:
  - name: WooramSeong
date: 05-14-2021
output:
  distill::distill_article:
    self_contained: false
    html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 5
    fig_height: 4
    theme: cosmo
    highlight: tango
    code_folding: code
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library, include=FALSE}
library(tidymodels)

library(tidyverse) 

library(skimr)

library(knitr)
```

```{r load table, include=FALSE}

  
  file_path <-  "/cloud/project/input"
  
  files <-list.files(file_path)
  
  files
  example_data <- read_csv(file.path(file_path, "Table1.csv"))
  colnames(example_data)
                    
```

## 2. Maximum Likelihood Estimator of Poisson Regression

(1)


```{r code1, include=TRUE}
model<-glm(Claims ~ Gender + Territory,
family = poisson(link=log), data = example_data)
model$coefficients


```

(2)
- Define Likelihood and Loglikelihood function
\
\
*Likelihood function* : $\prod_{i=1}^n  \frac{e^{-\lambda} + \lambda^{y_i}} {y_i!}$
\
\
*Loglikelihood function* : $\sum_{i=1}^n  -\lambda + y_i ln \lambda - ln y_i!$
\
\

- Calculate gradient of Loglikelihood function with repect to $\beta$
\
\
$\lambda=e^{x_i^{T}\beta}$
\
\
$\displaystyle \frac{\partial -l(\beta)}{\partial \beta} = \sum_{i=1}^n (y_i - e^{x_i^{T}\beta}) x_i^{T}$


```{r code11, include=FALSE}
example_data$Gender[example_data$Gender=="M"] <-1
example_data$Gender[example_data$Gender=="F"] <-0
example_data$Territory[example_data$Territory=="West"]<-1
example_data$Territory[example_data$Territory=="East"]<-0
example_data

example_data$Gender<-as.numeric(example_data$Gender)
example_data$Territory<-as.numeric(example_data$Territory)

class(example_data$Gender)

```


```{r code2, include=TRUE}
set.seed(2022)
beta <- rnorm(3)

sigma_f<-function(x){exp(x)}


nll <- function(beta){
  y<- example_data$Claims
  pi_vec <- sigma_f(matrix(cbind(1, example_data$Gender,
                                    example_data$Territory),ncol = 3) %*% matrix(beta, nrow = 3))
  -sum((-pi_vec)+y*log(pi_vec)-log(factorial(y)))
}
```

```{r code3, include=TRUE}
grad_nll <- function(beta){
y<- example_data$Claims
xbeta <- matrix(cbind(1,example_data$Gender,example_data$Territory),ncol=3) %*% beta
pi_vec <- sigma_f(xbeta)
-colSums(as.vector(y-pi_vec)*matrix(cbind(1,example_data$Gender,example_data$Territory),ncol=3))
}
grad_nll(beta)
```

```{r code4, include=TRUE}
set.seed(2022)
beta<-rnorm(3)
iter_n <-1
improve <-1
conv_threshold <- 1e-15
max_n <- 100000
result <- matrix(0, nrow = max_n, ncol = 3)
while ((improve > conv_threshold) & (iter_n<= max_n)) {
  beta_new <- beta - 0.001 * grad_nll(beta)
  improve <- abs(nll(beta)-nll(beta_new))
  result[iter_n,]<- beta_new
  beta <- beta_new
  iter_n <- iter_n +1
}

result[iter_n-1,]
model$coefficients
```





